%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{NA}{Company}
\date{\today}
\opening{Dear NA,}
\closing{Sincerely,}
%\enclosure[Attached]{r\'{e}sum\'{e}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I would like to express my interest in the Course Management Systems Analyst position.
I believe it will be a great opportunity for me to expand on the foundation of skills
that my current position has given me. I have been at LCC for a little over eight years,
the majority of which has been at the IT Help Desk. Based on my experience and knowledge
of LCC's procedures and systems I know that I would be a great addition to the eLearning team.

For the past eight years I have loved working in the ITS Department and it has afforded me
numerous opportunities for both professional and personal growth. Many of the skills I have
gained during my time at the Help Desk translate well to the analyst position. It would also
allow me to develop new skills. Through supporting students and staff I have become quite
knowledgeable on various aspects of D2L and familiar with a number of associated systems.
Being in a support role has also taught me patience and how to break down processes into
real world terms that are easy to understand.

In addition to my responsibilities as part of the IT Help Desk, my current ongoing
project is upgrading, maintaining, and expanding the use of LCC's ticketing system
in other departments. I have also attended conferences and worked with TeamDynamix
vendors in an effort to resolve issues and learn new enterprise service management
methods to better serve LCC's community. After attending an informative presentation
at a conference last year I was inspired to make some of my duties more efficient by
utilizing the ticketing system API. Outside of work I started reading and doing Python
tutorials to be able to interact with the API and streamline some of the more repetitive
tasks. I am now currently working on semi-automating the process of entering new hires
and terminations when I have spare time from my other duties. I am also currently
working with the other administrators to bring Facilities into the ticketing system
and away from a system that no longer has support.

I believe that the services eLearning provides to the community are invaluable
and I am excited to offer my skills in support of their goals towards overall success.

Thank you in advance for considering my application and I look forward to speaking with you.


\makeletterclosing
